A distance metric between histograms through the the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses

### 2015-10-31 paper.tex
melhoradas formatacoes das tabelas

% Input tables
% any plot? If std is ~stable, plots of the mean of c~(\alpha) are compact and informative
\input{tables/tabNormNull}
\input{tables/tabUniformNull}
\input{tables/tabWeibullNull}
\input{tables/tabPowerNull}

\FloatBarrier
\subsection{When the null hypothesis if false}
The null hypothesis is always false for a sufficiently small
significance level $\alpha$.
In this section,
each table holds a set comparisons between two samples:
one sample is generated through a
fixed distribution while the other
sample is modified in each comparison.
The comparison is repeated $N_c$ times.
The measures on $c$ chosen to report the results are:
the mean $\mu(c)$, the standard deviation $\sigma(c)$,
the median $m(c)$,
the  fraction
$\overline{C(\alpha)}=\frac{|C(\alpha)|}{N_c}$
of rejection of the null hypothesis with critical region $\alpha$.

\input{tables/tabNormDiff3}
\input{tables/tabNormDiffMean}
\input{tables/tabUniformDiffSpread}
\input{tables/tabUniformDiffMean}
\input{tables/tabWeibullDiffShape}
\input{tables/tabPowerDiffShape}
%\input{tables/tabNormDiff1}
%\input{tables/tabNormDiff2}

>>>>

% Input tables
% any plot? If std is ~stable, plots of the mean of c~(\alpha) are compact and informative
\input{tables/tabNormNull_}
\input{tables/tabUniformNull_}
\input{tables/tabWeibullNull_}
\input{tables/tabPowerNull_}

\FloatBarrier
\subsection{When the null hypothesis if false}
The null hypothesis is always false for a sufficiently small
significance level $\alpha$.
In this section,
each table holds a set comparisons between two samples:
one sample is generated through a
fixed distribution while the other
sample is modified in each comparison.
The comparison is repeated $N_c$ times.
The measures on $c$ chosen to report the results are:
the mean $\mu(c)$, the standard deviation $\sigma(c)$,
the median $m(c)$,
the  fraction
$\overline{C(\alpha)}=\frac{|C(\alpha)|}{N_c}$
of rejection of the null hypothesis given the significance level $\alpha$.
The null hypothesis is true in the boldface lines.

\input{tables/tabNormDiff3_}
\input{tables/tabNormDiffMean_}
\input{tables/tabUniformDiffSpread_}
\input{tables/tabUniformDiffMean_}
\input{tables/tabWeibullDiffShape_}
\input{tables/tabPowerDiffShape_}
%\input{tables/tabNormDiff1}
%\input{tables/tabNormDiff2}

### 2015-10-31 tables/tabNormNull_.tex
melhoradas formatacoes das tabelas

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 3 & 3 & 9 \\\hline
5.0 & 0.050 & 1.36 & 1 & 2 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for significance levels $\alpha$.
The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.6527$ and $\sigma(c_1)=0.2398$,
 $\mu(c_2)=0.6889$ and $\sigma(c_2)=0.2397$,
 $\mu(c_3)=0.7184$ and $\sigma(c_3)=0.2811$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 0 & 0 & 4 \\\hline
5.0 & 0.050 & 1.36 & 0 & 0 & 2 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 2 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for significance levels $\alpha$.
The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.6713$ and $\sigma(c_1)=0.2157$,
 $\mu(c_2)=0.6706$ and $\sigma(c_2)=0.2048$,
 $\mu(c_3)=0.6930$ and $\sigma(c_3)=0.2627$ .
}
\end{center}
\end{table}

### 2015-10-31 tables/tabPowerNull_.tex
melhoradas formatacoes das tabelas

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 5 & 5 & 7 & 5 & 5 \\\hline
5.0 & 0.050 & 1.36 & 2 & 3 & 5 & 1 & 1 \\\hline
2.5 & 0.025 & 1.48 & 1 & 2 & 1 & 1 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.6883$ and $\sigma(c_1)=0.2617$,
 $\mu(c_2)=0.7701$ and $\sigma(c_2)=0.2432$,
 $\mu(c_3)=0.7871$ and $\sigma(c_3)=0.2592$ .
 $\mu(c_4)=0.7721$ and $\sigma(c_4)=0.2587$ .
 $\mu(c_5)=0.7008$ and $\sigma(c_5)=0.2463$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 1 & 6 & 4 & 4 & 5 \\\hline
5.0 & 0.050 & 1.36 & 1 & 2 & 2 & 1 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 0 & 1 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.7017$ and $\sigma(c_1)=0.2390$,
 $\mu(c_2)=0.7612$ and $\sigma(c_2)=0.2575$,
 $\mu(c_3)=0.7708$ and $\sigma(c_3)=0.2594$ .
 $\mu(c_4)=0.7234$ and $\sigma(c_4)=0.2318$ .
 $\mu(c_5)=0.7504$ and $\sigma(c_5)=0.2626$ .
}
\end{center}
\end{table}

### 2015-10-31 tables/tabUniformNull_.tex
melhoradas formatacoes das tabelas

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.7656$ and $\sigma(c_1)=0.2552$,
 $\mu(c_2)=0.7520$ and $\sigma(c_2)=0.2421$,
 $\mu(c_3)=0.7077$ and $\sigma(c_3)=0.2250$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 6 & 3 & 4 \\\hline
5.0 & 0.050 & 1.36 & 4 & 1 & 3 \\\hline
2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.7735$ and $\sigma(c_1)=0.2591$,
 $\mu(c_2)=0.7337$ and $\sigma(c_2)=0.2412$,
 $\mu(c_3)=0.7558$ and $\sigma(c_3)=0.2315$ .
}
\end{center}
\end{table}

### 2015-10-31 tables/tabWeibullNull_.tex
melhoradas formatacoes das tabelas

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 2 & 0 & 4 \\\hline
5.0 & 0.050 & 1.36 & 0 & 1 & 0 & 1 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.0548$ and $\sigma(c_1)=0.0314$,
 $\mu(c_2)=0.6878$ and $\sigma(c_2)=0.2352$,
 $\mu(c_3)=0.7030$ and $\sigma(c_3)=0.2037$ .
 $\mu(c_4)=0.7350$ and $\sigma(c_4)=0.2510$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline\hline
10.0 & 0.100 & 1.22 & 0 & 4 & 3 & 8 \\\hline
5.0 & 0.050 & 1.36 & 0 & 0 & 1 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1)=0.0655$ and $\sigma(c_1)=0.0376$,
 $\mu(c_2)=0.7053$ and $\sigma(c_2)=0.2261$,
 $\mu(c_3)=0.6905$ and $\sigma(c_3)=0.2460$ .
 $\mu(c_4)=0.7596$ and $\sigma(c_4)=0.2644$ .
}
\end{center}
\end{table}
